---
title: "Fraud Detection"
date: "`r Sys.Date()`"
author: Ana Córdova, David Cornejo, Ramón Escobar, Katherine Palacios, Andrea Velásquez
output:
  rmdformats::html_clean:
    highlight: kate
---
```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

options(max.print="75")
opts_chunk$set(echo=T,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

# Modeling Fraud Dtection looking for max AIC
## Importing packages
```{r, message=FALSE, results='hide', warning=FALSE}
library(corrplot)
library(RColorBrewer)
library(forecast)
library(gains)
library(caret)
library(ROCR)
library(leaps)
library(bestglm)
library(dplyr)
library(ggplot2)
```

## Importing and balancing the data
```{r}
set.seed(3997)
fraud.df<-read.csv(file.choose())
isNotFraud.df<-fraud.df %>%
  filter(isFraud==0)
isFraud.df<-fraud.df %>%
  filter(isFraud==1)
selected.index<-sample(c(1:276241),800)
isNotFraud.df<-isNotFraud.df[selected.index,]

fraud.df<-rbind(isNotFraud.df,isFraud.df)
```

## Factoring and adding variables
```{r}
fraud.df$type<-as.factor(fraud.df$type)
fraud.df$isFlaggedFraud<-factor(fraud.df$isFlaggedFraud,
                                levels = c(0,1))
fraud.df$isFraud<-factor(fraud.df$isFraud,
                         levels=c(0,1))
fraud.df$diff.orig<-fraud.df$oldbalanceOrg-(fraud.df$newbalanceOrig)
fraud.df$diff.dest<-fraud.df$newbalanceDest-(fraud.df$oldbalanceDest)
fraud.df$Hours<-(fraud.df$step)%%24
```

## Deleting some variables
```{r}
fraud.df$step<-NULL
fraud.df$isFlaggedFraud<-NULL
fraud.df$nameOrig<-NULL
fraud.df$nameDest<-NULL
```

## Corr. of variables
```{r, echo=T}
mat_cor <- cor(x= fraud.df [,sapply(fraud.df, is.numeric)])
corrplot(mat_cor,
         type="upper",
         order="hclust",
         method = "number", 
         col=brewer.pal(n=8, name="RdYlBu"))
```
## Preliminar Analysis
```{r}
summary(fraud.df)
```

### Some graphics with distributions 
```{r}
ggplot(fraud.df, aes(isFraud,amount))+
  geom_boxplot() + ggtitle("Distribution of Amount filtered by isFraud")

ggplot(fraud.df, aes(Hours, amount))+
  geom_point() + ggtitle("Distribution of Amount filtered by Hours")

ggplot(fraud.df, aes(isFraud,Hours))+
  geom_boxplot() + ggtitle("Cross of isFraud and Hours")

ggplot(fraud.df, aes(isFraud, newbalanceDest))+
  geom_boxplot()+ggtitle("Cross of isFraud and newbalanceDest")

```

### Tables 
```{r}
table(fraud.df$type,fraud.df$isFraud)
table(fraud.df$Hours,fraud.df$isFraud)
```

## Creating Partition of data
```{r}
set.seed(3997)
train.index <- sample(x= c(1:nrow(fraud.df)), 
                      size= nrow(fraud.df)*0.8)

train.df <- fraud.df[train.index,]
valid.df <- fraud.df[-train.index,]
```

## Looking for max AIC
```{r, warning=F, error=FALSE}
train.df <-
  train.df[, c("Hours","type","amount","diff.dest","diff.orig","isFraud")]
res.bestglm <- bestglm(Xy = train.df,
                       family = binomial,
                       IC = "AIC",                 
                       method = "exhaustive")
```

```{r,results='hide'}
res.bestglm$BestModels
options(scipen = 999)
```
```{r}
summary(res.bestglm$BestModel)
```

### Modeling the data with Logit
```{r}
logit.reg <- glm(isFraud ~ Hours+type+amount+diff.dest+diff.orig, 
                 data = train.df, 
                 family = "binomial")
options(scipen=999)
summary(logit.reg)
```
### Odds og the model
```{r}
round(data.frame(summary(logit.reg)$coefficients, odds = exp(coef(logit.reg))), 5)
```

### R2 of the logit model
```{r}
basereg <- glm(isFraud ~ 1, data = train.df, family = "binomial")
1-(logLik(logit.reg))/(logLik(basereg))
```

### ROC Curve
```{r}
logit.reg.pred <- predict(logit.reg, valid.df, type = "response")
pred <- prediction(logit.reg.pred, valid.df$isFraud)
perf <- performance(pred, measure = "tpr", x.measure = "fpr") 
par(mar=c(5,5,2,2),xaxs = "i",yaxs = "i",cex.axis=1.3,cex.lab=1.4)
plot(perf, col=rainbow(10))
abline(a=0, b= 1)
auc <- round(as.numeric(performance(pred,"auc")@y.values),2)
auc_value <- paste("AUC= ", auc, sep="")
legend(0.7,0.2,auc_value,border="white",cex=1,box.col = "white")
grid(nx = 10, ny = NULL, col = "lightgray", lty = "dotted")
```

## Cutoff, Recall and other measures
```{r}
pred <- prediction(logit.reg.pred, valid.df$isFraud)
perf <- performance(pred, x.measure = "prec", measure = "rec")

opt.cut = function(perf, pred){
  cut.ind = mapply(FUN=function(x, y, p){
    d = (2*(x*y))/(x+y)
    ind = min(which(d == max(d, na.rm=TRUE)))
    c(recall = y[[ind]], precision = x[[ind]], 
      cutoff = p[[ind]], f1score= max(d, na.rm=TRUE))
  }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(perf, pred))

```

## Confussion Matrix
```{r}
cutoff <- opt.cut(perf, pred)[3]
CM <- confusionMatrix(data= as.factor(ifelse(logit.reg.pred > cutoff, 1, 0)), 
                      reference= as.factor(valid.df$isFraud),
                      positive= "1",
                      mode= "prec_recall")
t(CM$table)
options(scipen=999)
CM$byClass
```